### 2017-12-11 submission/supplemental.Rmd
add table s4

**Table S4: **

@@

>>>>

**Table S4: Tukey Post-Hoc Results of Number of OTUs Differences between HiFi Taq in Mock Samples**

@@

mock_tukey <- as.data.frame(read_csv("../data/process/tables/mock_overall_tukey_results.csv")) %>% 
  mutate_at(vars(diff:upr), funs(round(., digits = 2))) %>% 
  rename(padj = `p adj`) %>% 
  mutate(padj = as.numeric(padj)) %>% 
  filter(padj < 0.05, sub_sample_level > 500) %>% 
  arrange(padj) %>% 
  mutate_at(vars(padj), funs(format(., scientific = TRUE, digits = 2, nsmall = 2)))

colnames(mock_tukey) <- c("Difference", "Lower", "Upper", "P Adjusted", "Comparison", "Cycle", "Sub-Sample Depth")

kable(mock_tukey, format = "markdown", align = 'c', padding = 2)
